### 2016-04-23 manuscript-body.tex
Enhance Wil's conclusion

>>>>

\section{Conclusion}

In this article, we have argued for expanding our cognitive models beyond misconceptions in computing education research. We

\begin{enumerate}
  \tightlist
  \item Reanalyzed historical data through the perspective of productive student knowledge, building evidence in classic computing education research that we can recover novice's productive knowledge without simply labeling it as non-canonical or wrong
  \item Explored several examples that reveal both the adaptive nature of computing expertise and the power of non-misconception frameworks---namely distributed cognition and knowledge-in-pieces/symbolic forms.
  \item Stressed that models to what counts as knowledge and knowing have both historical success in other fields and obvious implications for computing education
\end{enumerate}

Ultimately, the modeling of cognition only or primarily as a set of privileged, canonical knowledge and how students do or don't have it is eclipsing the other productive knowledge and ways of knowing that students do have. While useful, misconceptions can only take us so far in our efforts to understand and improve learning in computing education.
